Hydras \& Co.

### 2022-04-06 doc/gaia-chapter.tex
simplification of notations in theories/gaia

Many constants are common to \HydrasLib and \gaia. The following notations allow us to get rid of possible ambiguities, still
keeping with the prefix convention: ``h'' for \HydrasLib, ``g'' for \gaia.

@@

>>>>

Many constants are common to \HydrasLib and \gaia. For instance, the name \texttt{zero} may refer to \gaia's
\texttt{gaia.ssete9.CantorOrdinal.zero}  and
\HydrasLib' \texttt{hydras.Epsilon0.T1.zero}. By default, the former will be simply called \texttt{zero} and the latter \texttt{T1.zero}.

There are a few exceptions to this convention.

@@

\begin{table}[H]
  \centering
  \begin{threeparttable}
    \caption{Main constants}
\begin{tabular}{|r | c|c|c|c|l|}
\hline
Hydras & page & Gaia-Hydras& page& Description \\\hline
  \texttt{T1.zero}
       &  \pageref{types:T1}
              & \texttt{CantorOrdinal.zero \tnote{1}}
                           &  & The ordinal $0$  \\

\hline
\end{tabular}
\begin{tablenotes}
  \item[1] From \gaia library.
   \item[2] From \ssreflect/\mathcomp libraries.
\end{tablenotes}
\end{threeparttable}
\end{table}
